A Short and Mechanized Consistency Proof for Dependent Type Theory

### 2024-02-14 paper/paper.tex
Use array for semtyping definitions

\section{Semantic Typing and Consistency}
\label{sec:logrelproof}
\begin{figure}[h]
  \begin{equation*}
    \begin{split}
      [[rho |= G]] &:= \forall i\ j\ S, \text{ if }[[i < |G|]]\text{ and
                     } [[InterpR j (up Suc i G i) { rho } S ]] \text{, then } [[rho i in S]] \\
      [[G |= a : A]] &:= \forall [[rho]], \text{ if }[[rho |=
                       G]]\text{ then there exists some } [[j]] \text{
                       and } [[S]] \text{ such that } [[InterpR j A
                       {rho} S]] \text{ and } [[a {rho} in S]] \\
      [[|= G]] &:= \forall [[i < |G|]], \exists [[j]], [[drop Suc i G |= G i : Set j]]
    \end{split}
  \end{equation*}
  \caption{Semantic Typing for \lang}
  \label{fig:semtyping}
\end{figure}

@@

>>>>

\section{Semantic Typing and Consistency}
\label{sec:logrelproof}
\begin{figure}[h]
\[
\begin{array}{lcl}

      [[rho |= G]] &:= & \forall i\ j\ S, \text{ if }[[i < |G|]]\text{ and
                     } [[InterpR j (up Suc i G i) { rho } S ]] \text{, then } [[rho i in S]] \\
      [[G |= a : A]] &:= & \forall [[rho]], \text{ if }[[rho |=
                       G]]\text{ then there exists some } [[j]] \text{
                       and } [[S]] \text{ such that } [[InterpR j A
                       {rho} S]] \text{ and } [[a {rho} in S]] \\
      [[|= G]] &:= & \forall [[i < |G|]], \exists [[j]], [[drop Suc i G |= G i : Set j]]
\end{array}
\]
  \caption{Semantic Typing for \lang}
  \label{fig:semtyping}
\end{figure}

@@

\section{Conclusion}
\label{sec:conclusion}
